%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt,letterpaper,roman]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

%\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Caleb} % Your first name
\familyname{Logemann} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vit\ae{}}
\address{396 Carver Hall, 411 Morrill Road}{Ames, IA 50011}
%\mobile{(000) 111 1111}
\phone{(515) 494 7256}
%\fax{(000) 111 1113}
\email{logemann@iastate.edu}
\homepage{caleblogemann.github.io}{caleblogemann.github.io} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%   COVER LETTER
%----------------------------------------------------------------------------------------
  % To remove the cover letter, comment out this entire block

  %\clearpage

  %\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
  %\date{\today} % Letter date
  %\opening{Dear Sir or Madam,} % Opening greeting
  %\closing{Sincerely yours,} % Closing phrase
  %\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

  %\makelettertitle % Print letter title

  %\lipsum[1-2] % Dummy text
  %\lipsum[4] % Dummy text

  %\makeletterclosing % Print letter signature

  %\newpage
%----------------------------------------------------------------------------------------
%   CURRICULUM VITAE
%----------------------------------------------------------------------------------------
\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
  \cventry{2015--Present}{Masters/Ph.D.}{Iowa State University}{Applied Mathematics}{GPA --- 3.88}{Graduate Minor: Aerospace Engineering}
  \cventry{2011--2015}{Bachelor of Arts}{Bethel University}{GPA --- 3.96}{ Majors --- Mathematics, Physics, Computer Science}{Honors Program}

\section{Research}
\cventry{2016--Present}{Computational Mathematics}{Dr.\ James Rossmanith}{Iowa State University}{}{
  \begin{itemize}
    \item Developed new stable and high order numerical methods for solving thin film equations.
      Detailed acheivements:
      \begin{itemize}
        \item Adapted the Local Discontinuous Galerkin method to solve the thin film equation.
        \item Developed C++ software to compute said methods in \textsc{DogPack} software package
        \item Used preconditioners and the geometric multigrid method to accelerate solver
        % TODO: Add statement about Picard iteration
      \end{itemize}
    \item Developing high-order discontinuous Galerkin methods for the shallow water equations on the sphere with an icosahedral mesh.
      Pursuing method for generalized shallow water equations with vertical structure.
  \end{itemize}
}

\cventry{Summer 2019}{Computational Fluid Mechanics}{Dr.\ Travis Fisher}{\textsc{Sandia National Labs}}{Albuquerque, NM}{
  Explored Error Transport techniques using Defect Correction method for Hyperbolic
  Conservation Laws.
  Detailed achievements:
  \begin{itemize}
    \item Developed model for the truncation error
    \item Used Summation By Parts (SBP) Finite Difference Operators
    \item Presented work in oral and written report
  \end{itemize}
}

\cventry{2015}{Mathematical Neuroscience}{Dr.\ Brian Turnquist}{Bethel University}{}{
  Researched the developement of new mathematical techniques for quantifying and
  classifying neural data.
  Developed efficient algorithms for computing said mathematical techniques.
  Detailed acheivements:
  \begin{itemize}
    \item Created novel use of silhouette statistic to differentiate neural
      responses to itch and pain.
    \item Developed efficient algorithms for computing said statistic by
      incorporating genetic algorithms.
  \end{itemize}
}

\cventry{2014}{NanoOptics}{Dr.\ Nathan Lindquist}{Bethel University}{}{
  Researched the creation of a scattering based optical trap for the control of
  mirco particles.
  \newline{}
  Detailed achievements:
  \begin{itemize}
    \item Developed LabView software to control and monitor the focus of the
      laser.
    \item Measured the strength of the trap.
    \item Optimized the strength of the trap.
  \end{itemize}
}

\cventry{2013}{Atomic and Molecular Optics}{Dr.\ Chad Hoyt}{Bethel University}{}{
  Individually researched the developement of a cheap and portable iodine spectroscopy setup
  which could be used as locked absolute reference in the frequency space.
  Also collaborated with group working on trapping cold lithium in magneto-optical trap.
  \newline{}
  Detailed achievements:
  \begin{itemize}
    \item Built and fine-tuned a enclosed cavity diode laser.
    \item Calibrated apparatus to acheive maximum interaction between the laser
      and the iodine.
    \item Built and tested circuitry for the precise measurement of the temperature of lithium.
  \end{itemize}
}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Professional Experience}
\cventry{2015--Present}{Graduate Teaching Assistent}{\textsc{Iowa State University}}{
  Ames, IA}{}{Taught undergraduate recitations in mathematics.
  \newline{}
  Detailed achievements:
  \begin{itemize}
    \item Worked closely with professors to develop class materials.
    \item Taught one hour lectures in Calculus and Differential Equation to
      smaller sections of students.
    \item Guided students through a team based learning (TBL) approach to Precalculus.
  \end{itemize}
}

\cventry{Summer 2017}{Graduate Mentor of Undergraduate Research}{\textsc{Iowa State University}}{
  Ames, IA}{}{Lead and mentored group of four undergraduate students in computational
  research
  \newline{}
  Detailed achievements:
  \begin{itemize}
    \item Advised students in research techniques
    \item Explored Space-Time/Lax-Wendroff Discontinuous Galerkin Method
    \item Developed positivity preserving limiters and oscillation limiters
  \end{itemize}
}

\cventry{2014--2015}{Intern Software Developer}{\textsc{Relationship One}}{
  Minneapolis, MN}{}{Developed Java based sofware in an agile software developement environment.
  \newline{}
  Detailed achievements:
  \begin{itemize}
    \item Created Java applications to assist companies in managing their costumer data.
    \item Used advanced Javascript and HTML for the continued developement of company website.
    \item Integrated web application with a SQL Database through a Node.js server.
  \end{itemize}
}

\section{Projects}
\cventry{2016--Present}{DoGPack Developer}{Iowa State University}{}{}{
  Developed additions to C++ package for solving Hyperbolic Conservation Laws
  with Discontinuous Galerkin Method.
  Detailed Achievements:
  \begin{itemize}
    \item Utilized design patterns to limit code reuse
    \item Added unit testing framework
    \item Experienced with version control systems
  \end{itemize}
}

\cventry{2016}{MATH 610 Early Graduate Research}{Iowa State University}{}{}{
  Expanded on Stochastic Galerkin Method for Hamilton-Jacobi Equations.
  Detailed Achievements:
  \begin{itemize}
    \item Uncertainty Quantification through Stochastic expansion of Galerkin Method
    \item Utilized Runge Kutta IMEX time stepping scheme
    \item Implemented method in MATLAB
  \end{itemize}
}

% Add project about reinforcement learning

\section{Leadership Experience}
\cventry{2017--2019}{President, SIAM, Iowa State Chapter}{}{}{}{
  Student President of the Iowa State Chapter of the Society for Industrial and
  Applied Mathematics.
  Detailed Achievements:
  \begin{itemize}
    \item Lead seminar for graduate students interested in Applied Math
    \item Organized student trips to SIAM Central States Sectional Meetings
    \item Advised younger graduate students
  \end{itemize}
}

\section{Publications}
\cventry{2018}{C. Felton, M. Harris, C. Logemann, S. Nelson, I. Pelakh, and
  J. Rossmanith}{A Positivity-Preserving Limiting Strategy for Locally-Implicit
  Lax-Wendroff Discontinuous Galerkin Methods}{Advances in Computational
  Mathematics, Submitted, (arXiv: 1806.06756)}{}{}
\cventry{2019}{C. Logemann and J. Rossmanith}{An Implicit-Explicit Discontinuous
  Galerkin Scheme using a Newton-Free Picard Iteration for a Thin-Film Model}{In
  Preparation}{}{}
\cventry{2019}{C. Logemann and J. Rossmanith}{A Discontinuous Galerkin Method
  for Generalized Shallow Water Equations on the Sphere}{In Preparation}{}{}


\section{Invited and Contributed Talks}
\cvitem{2019}{SIAM Central States Section Meeting, \textit{An Implicit-Explicit Discontinuous Galerkin Scheme using a Newton-Free Picard Iteration for a Thin-Film Model}}
\cvitem{2019}{ISU Chapter of SIAM Seminar, \textit{Error Transport using the Defect Correction Equations with Summation By Parts Operators}}
\cvitem{2019}{SIAM Conference on Computational Science and Engineering, \textit{High Order Discontinuous Galerkin Scheme for Thin-Film Equations}}
\cvitem{2019}{Midwest Numerical Analysis Days, \textit{High Order Discontinuous Galerkin Scheme for Thin-Film Equations}}
\cvitem{2018}{Graduate Student Seminar at Iowa State University. \textit{Overview of Discontinuous Galerkin Methods}}
\cvitem{2017}{SIAM Central States Section Meeting, \textit{Local Discontinuous Galerkin Method for Thin-Film Equations}}


\section{Conferences Attended}
\cvitem{2016, 2018}{SIAM Central States Section Meeting}
\cvitem{2017, 2018}{Midwest Numerical Analysis Days}

\section{Computational and Applied Math Coursework}
\cvitem{}{MATH 561, 562 --- Numerical Analysis and Numerical Linear Algebra}
\cvitem{}{MATH 517, 666, 667 --- Finite Difference Methods, Finite Volume Methods, Finite Element Methods}
\cvitem{}{MATH 565, 566 --- Continuous and Discrete Optimization}
\cvitem{}{MATH 519, 520 --- Applied Analysis I and II}
\cvitem{}{AERE E 510, 546 --- Fluid Mechanics and Continuum Mechanics}
\cvitem{}{AERE E 504X --- Reinforcement Learning}
\cvitem{}{MATH 680 --- Regularity of Elliptic PDEs}

\section{Awards}
\cvitem{2019}{AMS Travel Grand --- JMM 2020}
\cvitem{2018}{SIAM Student Travel Award --- SIAM CSE 2019}
\cvitem{2012}{Richard Peterson Scholarship in Physics Recipient}
\cvitem{2013--2015}{Pamela Olson Math/Physics Scholarship Recipient}
% \cvitem{2013--2014}{Greuz Physics Scholarship Recipient}
\cvitem{2014--2015}{Anderson Math/Physics Scholarship Recipient}

% \section{ExtraCurricular Activities}

% \cvitem{2017--Present}{President, SIAM, Iowa State Chapter}
% \cvitem{2016--2017}{Communications Officer, SIAM, Iowa State Chapter}
% \cvitem{2015--Present}{Member - American Mathematical Society}
% \cvitem{2012--2015}{Member - Sigma Pi Sigma Honor Society}

\end{document}
